---
title: "T1.3 Tropical/Subtropical montane rainforests"
date: 6 May 2024
categories:
 - T1
 - valid
format:
 html: 
  code-tools:
   source: true
execute:
   echo: false
---

```{r setup}
#| warning: false
#| message: false
library(xml2)
library(terra)
library(magick)

here::i_am("map-info/T1_3.qmd")
out_folder <- here::here("gisdata", "indicative-maps-bundle","latest")

map_details_file <- paste(out_folder, "map-details.xml", sep = "/")
# file.exists(map_details_file)
map_details <- read_xml(map_details_file)
map_info <- map_details |> xml_find_first("//Map[@efg_code='T1.3']")
map_attrs <- map_info |> xml_attrs()
ds_doi <- map_info |> xml_find_first("Dataset-doi") |> xml_text()
downloaded_copy <- here::here("gisdata", "indicative-maps", ds_doi)
efg_details <- read_xml(dir(downloaded_copy,"xml", full.names = TRUE))
```

```{r}
#| output: asis
efg_details |> xml_find_first("//Short-description") |> xml_text() |> cat()
```

```{r}
#| output: asis

markdown_text <- sprintf("## Map description\n\n ***%1$s***\n\n%2$s.\n\n **Map code and version**: %3$s %4$s. **Available at** DOI:[%5$s](https://doi.org/%5$s)",
    map_info |> xml_find_first("Functional_group") |> xml_text(),
    map_info |> xml_find_first("Description") |> xml_text(),
        map_attrs["map_code"],
        map_attrs["map_version"],
       ds_doi 
)

cat(markdown_text)
```


## Thumbnail map

```{r}
thmbmap <- dir(downloaded_copy,"png", full.names = TRUE)
raw_img <- image_read(thmbmap)
image_ggplot(raw_img)
```



## Raster map

We check the list of map files in the compressed raster archive:

```{r}
rast_tar <- here::here(out_folder, "all-maps-raster-geotiff.tar.bz2")
```

Or, more directly, using map code and map version attributes:

```{r}
raster_name <- 
    sprintf("%s_%s.tif",
        map_attrs["map_code"],
        map_attrs["map_version"])
```

```{r}
#| eval: true
#| echo: false

# we use this internally to speed up some steps:
workdir <- here::here("sandbox", "latest")
if (!dir.exists(workdir))
    dir.create(workdir, recursive = TRUE)
```

Extract the data here (unless it already exists)
```{r}
if (!raster_name %in% dir(workdir))
    untar(rast_tar, files = raster_name, exdir = workdir)
```


We'll use the terra library to read the raster file
```{r}
selected_raster <- terra::rast(paste(workdir, raster_name, sep = "/"))

```

Summary of the raster layer according to `terra::rast`:

```{r}
selected_raster
```

```{r}
plot(selected_raster)
```


## Vector map

We follow similar steps for the vector files. 

We vector archive is here:

```{r}
vect_tar <- here::here(out_folder, "all-maps-vector-geojson.tar.bz2")
```

We select the map for this functional group using the map_code and map_version from the map details xml:

```{r}
vector_name <- 
    sprintf("%s_%s.json",
        map_info |> xml_attr("map_code"),
        map_info |> xml_attr("map_version"))
```

We uncompress this into the tempdir

```{r}
print(workdir)
if (!vector_name %in% dir(workdir))
    untar(vect_tar, files = vector_name, exdir = workdir)
```

```{r}
#| eval: true
selected_vector <- terra::vect(paste(workdir, vector_name, sep = "/"))

```

Summary of the raster layer according to `terra::vect`:

```{r}
#| eval: true
selected_vector
```

```{r}
#| eval: false
plot(selected_vector)
```